draft_yma

### 2021-12-14 draft_yma.Rmd
calculated Cp, BIC

```{r}
par(mfrow = c(2,7))

@@

**Q: do we need more descriptive analysis, visualization? rate of crime for each state?**
**there's a few duplicated cty, but different area, maybe diff place then? not sure**
they can't be the same... otherwise we have to recalculate some stuff...
duplicated(cdi[,2:3])
cdi %>% filter(cty == "Baltimor")
cdi %>% filter(cty == "St._Loui")

#### Full model predictors ok?

@@

The lambda from the transformation is 0.5454, so we will try to fit a square root transformation to y

@@

lambda_trans = MASS::boxcox(trans_fit)
optlam_trans = lambda_trans$x[which.max(lambda_trans$y)]
lambda_trans
```

@@

### Test based procedures

@@

I didn't include the full model here

**backward & both**

```{r}
# printing the 2 best models of each size. For example, the first two lines: print the best 2 models that have 2 variables (including intercept)
library(leaps)
Cp_b = leaps(x = model.matrix(fit_back)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "Cp")
Cp_b

Cp_b %>% faraway::Cpplot()
```

@@

**forward**
```{r}
leaps(x = model.matrix(fit_forward)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "Cp") %>% faraway::Cpplot()
```

@@

**backward**
```{r}
adjr_b = leaps(x = model.matrix(fit_back)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "adjr2")

@@

adjr_b%>% 
  faraway::maxadjr(10)
```

**forward**
```{r}
leaps(x = model.matrix(fit_forward)[,-1],
      y = cdi_model$crm_1000,
      nbest = 2,
      method = "adjr2") %>% faraway::maxadjr(10)
```

>>>>

```{r boxplot}
par(mfrow = c(2,7))

@@

**Q: do we need more descriptive analysis, visualization? rate of crime for each state?**

#### Full model predictors

@@

The lambda from the transformation is 0.5454, so we will try to fit a square root transformation to Y

@@

lambda_trans = MASS::boxcox(trans_fit)
optlam_trans = lambda_trans$x[which.max(lambda_trans$y)]
lambda_trans

cdi_trans = cdi_model %>% mutate(crm_1000_sqr = crm_1000^0.5) %>% select(-c(crm_1000))
```

@@

### Criterion

@@

```{r}
olsrr::ols_mallows_cp(fit_back,trans_fit)
olsrr::ols_mallows_cp(fit_forward,trans_fit)
olsrr::ols_mallows_cp(fit_both,trans_fit)
```

```{r}
summary(fit_back) # 0.5469
summary(fit_forward) #0.5457
summary(fit_both) #5469
```

### BIC

```{r}
library(flexmix)
BIC(fit_back)
BIC(fit_forward)
BIC(fit_both)
```

## Cp

didn't use any of this!
```{r, include=FALSE}
# printing the 2 best models of each size. For example, the first two lines: print the best 2 models that have 2 variables (including intercept)
library(leaps)
Cp_b = leaps(x = model.matrix(trans_fit)[,-1],
      y = cdi_trans$crm_1000_sqr,
      nbest = 2,
      method = "Cp")

mod_b = Cp_b$Cp[which(Cp_b$Cp <= Cp_b$size)]
```

@@

**forward**
```{r, include=FALSE}
Cp_f = leaps(x = model.matrix(fit_forward)[,-1],
      y = cdi_trans$crm_1000_sqr,
      nbest = 2,
      method = "Cp")

mod_f = Cp_f$Cp[which(Cp_f$Cp <= Cp_f$size)]
```

@@

Did not use!!
**backward**
```{r, include=FALSE}
adjr_b = leaps(x = model.matrix(fit_back)[,-1],
      y = cdi_trans$crm_1000_sqr,
      nbest = 2,
      method = "adjr2")

@@

adjr_b%>% 
  faraway::maxadjr(10)
```
**forward**
```{r, include=FALSE}
leaps(x = model.matrix(fit_forward)[,-1],
      y = cdi_trans$crm_1000_sqr,
      nbest = 2,
      method = "adjr2") %>% faraway::maxadjr(10)
```
